---
title: "Comparison of AquaCrop Simulated and Field Measured Maize Canopy Cover"
author: "Rupinder Sandhu"
date: "5/1/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## AquaCrop

AquaCrop is a water driven model. the model was evaluated for its performance in simualting maize canopy cover in Nebraska. After appropriate calibration of the model, th field measured canopy cover datasets were compared with the model outputs. In this paper, the model results are presented for two growing seasons of 2009 and 2010. For more details on the model calibration and evaluation procedures see <https://doi.org/10.1016/j.agwat.2019.105687>.



```{r,}
# Reading the data file from the existing directory
canopycover=read.csv(file = "cc_aquacrop_results.csv",header = TRUE) 
```

```{r,}
# Reading few observations
head (canopycover)

#reading treatments in the data
#canopycover$Trt

#creating data frames for individual years
cc2009=canopycover[(canopycover$Year=="2009"),]
cc2010=canopycover[(canopycover$Year=="2010"),]

```

## Canopy cover for 2009 growing season
The model closely simulated the maize canopy cover in all treatments in 2009 growing season throughout the growing season indicating that good agreement between simulated and measured data. 

```{r ,}
## PLotting canopy cover for individual years and treatments
# Visualizing 2009 results 
layout(matrix(1:5, ncol = 1), widths = 1,respect = FALSE)
par(mar=c(0,7,0,2), mgp=c(5.0,1,0))
plot(Sim~ DAP,data=cc2009,font.lab=1,type="o",xaxt='n',ylab = "",xlab = "Days after planting (DAP)",cex.sub=1.2,font=2,xlim=c(0,150),ylim=c(0,105),subset=Trt=="0",cex.axis=1.2,cex=0, lwd=3, col="red")
points(Obs~ DAP,data=cc2009,font=2,subset=Trt=="0",cex=1.5, pch=19, col="black")
legend(100,55,legend= c("Simulated","Observed"),col=c("red","black"),lwd=c(3,NA),bty="n",pch=c(NA,19),cex=1.2)
text(10,80,"Rainfed", pch=17, cex=1.5)
     
#par(mar=c(0,7,0,2), mgp=c(3.0,1,0))
#plot(Sim~ DAP,data=cc2009,type="o",ylab = "",xaxt='n',xlab = "Days after planting (DAP)",cex.sub=1.2,font=2,xlim=c(0,150),ylim=c(0,105),subset=Trt=="50",cex.lab=1.2,cex.axis=1.2,cex=0, lwd=3,pch=1, col="red")
#points(Obs~ DAP,data=cc2009,font=2,subset=Trt=="50",cex=1.5, pch=19, col="black")
#text(10,80,"50%", pch=17, cex=1.8)

par(mar=c(0,7,0,2), mgp=c(3.0,1,0))
plot(Sim~ DAP,data=cc2009,type="o",ylab = "",xaxt='n',xlab = "Days after planting (DAP)",cex.sub=1.2,font=2,xlim=c(0,150),ylim=c(0,105),subset=Trt=="60",cex.lab=1.2,cex.axis=1.2,cex=0, lwd=3,pch=1, col="red")
points(Obs~ DAP,data=cc2009,font=2,subset=Trt=="60",cex=1.5, pch=19, col="black")
text(10,80,"60%", pch=17, cex=1.8)

#par(mar=c(0,7,0,2), mgp=c(3.0,1,0))
#plot(Sim~ DAP,data=cc2009,type="o",ylab = "",xaxt='n',xlab = "Days after planting (DAP)",cex.sub=1.2,font=2,xlim=c(0,150),ylim=c(0,105),subset=Trt=="75",cex.lab=1.2,cex.axis=1.2,cex=0, lwd=3,pch=1, col="red")
#points(Obs~ DAP,data=cc2009,font=2,subset=Trt=="75",cex=1.5, pch=19, col="black")
#text(10,80,"75%", pch=17, cex=1.8)

par(mar=c(0,7,0,2), mgp=c(3.0,1,0))
plot(Sim~ DAP,data=cc2009,type="o",ylab = "",xaxt='n',xlab = "Days after planting (DAP)",cex.sub=1.2,font=2,xlim=c(0,150),ylim=c(0,105),subset=Trt=="100",cex.lab=1.2,cex.axis=1.2,cex=0, lwd=3,pch=1, col="red")
points(Obs~ DAP,data=cc2009,font=2,subset=Trt=="100",cex=1.5, pch=19, col="black")
axis (1,font=2,at=c(0,20,40,60,80,100,120,140,155),cex.axis=1.8,labels=c(0,20,40,60,80,100,120,140,155))
text(10,80,"100%", pch=17, cex=1.8)
```


## Canopy cover for 2010 growing season
The model closely simulated the maize canopy cover in all treatments in 2010 growing season throughout the growing season except for the early maize growth stages. There was high disaggrement between simulated and measured data at the initial growth stages. 

```{r ,}
## PLotting canopy cover for individual years and treatments
# Visualizing 2009 results 
layout(matrix(1:5, ncol = 1), widths = 1,respect = FALSE)
par(mar=c(0,7,0,2), mgp=c(5.0,1,0))
plot(Sim~ DAP,data=cc2010,type="o",font.lab=1,xaxt='n',ylab = "",xlab = "Days after planting (DAP)",cex.sub=1.2,font=2,xlim=c(0,150),ylim=c(0,105),subset=Trt=="0",cex.lab=1.2,cex.axis=1.2,cex=0, lwd=3,pch=1, col="red")
points(Obs~ DAP,data=cc2010,font=2,subset=Trt=="0",cex=1.5, pch=19, col="black")
legend(100,55,legend= c("Simulated","Observed"),col=c("red","black"),lwd=c(3,NA),bty="n",pch=c(NA,19),cex=1.2)
text(10,80,"Rainfed", pch=17, cex=1.5)

#par(mar=c(0,7,0,2), mgp=c(3.0,1,0))
#plot(Sim~ DAP,data=cc2010,type="o",ylab = "",xaxt='n',xlab = "Days after planting (DAP)",cex.sub=1.2,font=2,xlim=c(0,150),ylim=c(0,105),subset=Trt=="50",cex.lab=1.2,cex.axis=1.2,cex=0, lwd=3,pch=1, col="red")
#points(Obs~ DAP,data=cc2010,font=2,subset=Trt=="50",cex=1.5, pch=19, col="black")
#text(10,80,"50%", pch=17, cex=1.8)

par(mar=c(0,7,0,2), mgp=c(3.0,1,0))
plot(Sim~ DAP,data=cc2010,type="o",ylab = "",xaxt='n',xlab = "Days after planting (DAP)",cex.sub=1.2,font=2,xlim=c(0,150),ylim=c(0,105),subset=Trt=="60",cex.lab=1.2,cex.axis=1.2,cex=0, lwd=3,pch=1, col="red")
points(Obs~ DAP,data=cc2010,font=2,subset=Trt=="60",cex=1.5, pch=19, col="black")
text(10,80,"60%", pch=17, cex=1.8)

#par(mar=c(0,7,0,2), mgp=c(3.0,1,0))
#plot(Sim~ DAP,data=cc2010,type="o",ylab = "",xaxt='n',xlab = "Days after planting (DAP)",cex.sub=1.2,font=2,xlim=c(0,150),ylim=c(0,105),subset=Trt=="75",cex.lab=1.2,cex.axis=1.2,cex=0, lwd=3,pch=1, col="red")
#points(Obs~ DAP,data=cc2010,font=2,subset=Trt=="75",cex=1.5, pch=19, col="black")
#text(10,80,"75%", pch=17, cex=1.8)

par(mar=c(0,7,0,2), mgp=c(3.0,1,0))
plot(Sim~ DAP,data=cc2010,type="o",ylab = "",xaxt='n',xlab = "Days after planting (DAP)",cex.sub=1.2,font=2,xlim=c(0,150),ylim=c(0,105),subset=Trt=="100",cex.lab=1.2,cex.axis=1.2,cex=0, lwd=3,pch=1, col="red")
points(Obs~ DAP,data=cc2010,font=2,subset=Trt=="100",cex=1.5, pch=19, col="black")
axis (1,font=2,at=c(0,20,40,60,80,100,120,140,155),cex.axis=1.8,labels=c(0,20,40,60,80,100,120,140,155))
text(10,80,"100%", pch=17, cex=1.8)
```


 
